\LaTeX\ Author Guidelines for ICCV Proceedings

### 2021-03-01 extra/rebuttal_CVPR/latex/egrebuttal.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{5813} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Rebuttal: GASP, a generalized framework for agglomerative clustering of signed graphs \\ and its application to Instance Segmentation}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

We thank the three reviewers for their helpful comments and for pointing out that our manuscript is very clear and well written (R1, R2, R3), is theoretically sound and provides a novel level of abstraction (R1) and is highly valuable in practice by achieving competitive accuracies on two publicly available benchmarks (R1, R3). \\

\textbf{Novelty and main contributions (R2, R3)} --
% Both R2 and R3 have raised questions regarding the novelty of our contribution. 
Our main contribution is GASP, a  framework that generalizes several existing and novel algorithms for agglomerative clustering of signed graphs, providing a powerful tool to study these methods.
R2 states that \emph{``exactly the same algorithms as GASP have been proposed''}, referring to GF [54] and GAEC [40]. 
Indeed, GF and GAEC are special cases of GASP, as we point out in Table 1 and lines 369-371. However, they are only two out of 14 algorithms described in our framework. In this paper we prove, for the first time, that Mutex Watershed [90] is another specialization of GASP -- an insight which we claim is nontrivial -- but all other algorithms are new at all, or at least in the context of signed graph partitioning. Indeed, one of the new algorithms, which on signed graphs has not been studied before, turns out to be the best among all variants we explored.
% Indeed, when using the sum linkage criterion, GASP is equivalent to GAEC (without cannot link constrants) or GF (with cannot link constraints) and we point out this relation in Table 1 and Section 3.3., lines 369-371. R2 also claims that \emph{``extension to include other linkage strategies is trivial''}, although, in our opinion, the fact that switching to another linkage criterion can be achieved with little changes shows one of the major strengths of our contribution: easy classification and comparison of agglomerative algorithms for signed graph clustering. Our framework can express the Mutex Watershed Algorithm [90] (so far never shown as agglomerative clustering algorithm), GAEC, and GF, as well as algorithms that, to the best of our knowledge, have not been studied systematically before, including signed graph clustering with average linkage.

R2 also states that \emph{``extension to include other linkage strategies is trivial''}. We agree wholeheartedly, and indeed consider this a great strength of the proposed framework, which allows an easy classification and comparison of agglomerative algorithms for signed graph clustering.

R3 points out that the use of signed graph clustering for instance segmentation is not novel and has been applied both in the context of natural images and EM connectomics. We agree, and cite pertinent prior work [42, 2, 7, 94]. Rather, we introduce a new framework that generalizes several existing methods and yields variants that have not been studied before. We believe that our contribution generates new insights into the utility of agglomerative clustering methods for Computer Vision and show their competitive performance when combined with predictions from neural networks, despite the fact that they are simple and efficient compared to other methods for signed graph partitioning. 
% Note that we cite important prior work, including several papers by the Hamprecht and Andres groups, who both have pioneered the use of signed graph clustering for instance segmentation.

\textbf{Comparison to multicut solvers (R2)} -- 
% R2 also quotes us as ``Authors say in lines 77-80 that no study has compared multicut solvers, while in fact there are plenty''. 
In lines 75-80 we write that \emph{``Agglomerative clustering algorithms for signed graphs have clear advantages: [...]. Despite the fact that a variety of these algorithms exist, no overarching study so far has been conducted to compare their robustness [...]''}. 
To the best of our knowledge, this claim pertaining to agglomerative algorithms is correct, and R2 does not offer references to the contrary.
% We do not claim, as suggested by R2, that there have not been any extensive studies for comparing \emph{multicut solvers}, but for \emph{agglomerative algorithms for signed graph clustering}. 
As R2 correctly points out, [54] contains an extensive evaluation of local search algorithms as multicut approximations, including the agglomerative methods GAEC and GF. However, [54] does not make a connection to agglomerative methods with different linkage criteria studied here. 
% Moreover, the other local search algorithms compared in [54] would not scale up well to the size of the problems studied in our work. 
Furthermore, R2 mentions the comparison of multicut solvers in [Beier et al., Cut, Glue \& Cut: A Fast, Approximate Solver for Multicut Partitioning]. We are aware of this work, but did not consider it sufficiently relevant in the context of our contribution, because it does not contain any comparison with agglomerative methods. Still, in the revised version we will cite it following R2.

\textbf{Experiments on larger graphs (R2)} --
R2 points out that we should conduct experiments on a broader set of problems and use graphs of larger size, referring to the experiments in [54]. We note that our experiments cover two important applications of instance segmentation from very different images (Cityscapes vs electron microscopy images) as well as clustering on random graphs, where we compare favorably to spectral methods. Regarding the problem size, note that the CREMI problem used for evaluation (Table 2) is solved on the pixel grid graph and contains $7\cdot 10^7$ nodes and $6\cdot 10^8$ edges, which is two orders of magnitude larger than the largest instance segmentation problem in [54] consisting of $10^5$ nodes and $10^7$ edges. In the revised version of the paper, we will add the specifications of the problem size on CREMI.

\textbf{Relevance of the results on CREMI (R2)} --
In the revised version, we will better define the CREMI score, which is given by the geometric mean of adapted Rand Error and Variation of Information, two commonly used metrics to evaluate clusterings. Given the small gap of 0.02 to the leading submission and the much bigger gap to other published methods, e.g. more than 0.3 gap for [95], it is fair to claim that we are competitive with state-of-the-art. In the revised version of the paper, we will comment on our standing in the CREMI leader-board.

\textbf{Clarifications about cityscapes experiments (R2)} --
R2 asks about the difference between the agglomeration method used in GMIS [63] and GASP. GMIS uses average linkage agglomerative clustering on an \emph{unsigned graph}, whereas GASP operates on a \emph{signed graph}. 
% As a consequence our algorithm can be applied without a hyper-parameter for the stopping criterion. 
In addition, as we point out in lines 769-771, the agglomeration procedure in GMIS is applied in multiple stages, which creates the need for further hyper-parameters and makes it more complex than our algorithm, which achieves comparable (slightly better) accuracy.

We have fine tuned the GMIS affinity predictions using the Dice Loss, which is a common approach to improve results for sparse spatial targets like affinities, see [90].

% {\small
% \bibliographystyle{ieee}
% \bibliography{egbib}
% }

\end{document}

### 2021-03-01 chapters/0_abstract.tex
Update to ECCV template
Update to CVPR2021 template
Small changes

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a new theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints. We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied before. 
On stochastic block model problems, GASP compares favorably to spectral clustering. More importantly, we conduct a systematic comparison of various instantiations of GASP in image instance segmentation problems, in terms of accuracy but also efficiency and robustness to noise. 
We find that one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset.
\end{abstract}

>>>>

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
\TODO{Update} We propose a new theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints. We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied before. 
On stochastic block model problems, GASP compares favorably to spectral clustering. More importantly, we conduct a systematic comparison of various instantiations of GASP in image instance segmentation problems, in terms of accuracy but also efficiency and robustness to noise. 
We find that one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset.
% \keywords{Partitioning of Signed Graphs, Generalized Framework, Agglomerative Clustering, Instance Segmentation}
\end{abstract}

### 2021-03-01 chapters/1_intro.tex
Small changes

\section{Introduction}
In computer vision, the partitioning of weighted graphs has been successfully applied to tasks as diverse as image segmentation, object tracking and pose estimation. 
Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes. These methods require users to specify the desired numbers of clusters (as in spectral clustering) or a termination criterion (e.g.\ in iterated normalized cuts) or even to add a seed for each object  (e.g.\ seeded watershed or random walker).

@@

In Sec.~\ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods on the task of neuron segmentation and how on synthetic graphs it achieves similar scores to a recently proposed spectral method for signed graphs. \TODO{Define HC and AC abbrv}

>>>>

\section{Introduction}
\TODO{Update} In computer vision, the partitioning of weighted graphs has been successfully applied to tasks as diverse as image segmentation, object tracking and pose estimation. 
Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes. These methods require users to specify the desired numbers of clusters (as in spectral clustering) or a termination criterion (e.g.\ in iterated normalized cuts) or even to add a seed for each object  (e.g.\ seeded watershed or random walker).

@@

In Sec.~\ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods on the task of neuron segmentation and how on synthetic graphs it achieves similar scores to a recently proposed spectral method for signed graphs. \TODO{Define HC abbrv}

### 2021-03-01 chapters/5_experiments_compare_rules.tex
Small changes

\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}[t]
\centering
    \begin{subfigure}[t]{0.47 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.25in 0.in 0.5in 0.in,clip]{./figs/SSBM_experiments.pdf}
        \caption{Scores on SSBM graphs}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.47 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
        \caption{Scores on \emph{CREMI-gridGraph} perturbed with noise}
    \end{subfigure}

    % \begin{subfigure}[t]{0.32 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
    % \end{subfigure}\hfill
    % \begin{subfigure}[t]{0.32 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
    % \end{subfigure}
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
    %     \caption{No long-range predictions: \\$p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    % \end{subfigure} \hfill
    % \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
    %     \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    % \end{subfigure}
\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions. Solid lines represent median values over 30 experiments. Values between the 25th and the 75th percentile are shown in shaded areas. The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph. Experiments are performed on a crop of CREMI training sample B.
\algname{} performances compared to spectral methods on synthetic graphs. The spectral methods were given the true number of clusters as input, in contrast to \algname{}. \TODO{Define paramters SSB; explain percentile stuff (for both noise experiments)}
}\label{fig:noise_plots}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.47\textwidth,trim=0.25in 0.in 0.5in 0.in,clip]{./figs/SSBM_experiments.pdf}
        \caption{Scores on SSBM graphs}
\end{figure}
\begin{figure}[t]
\centering
\includegraphics[width=0.47\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
        \caption{Scores on \emph{CREMI-gridGraph} perturbed with noise}
\end{figure}

% \captionsetup[subfigure]{justification=centering, singlelinecheck=off}
% \begin{figure}[t]
% \centering
%     \begin{subfigure}[t]{0.47 \textwidth}
%         \centering
%         \includegraphics[width=\textwidth,trim=0.25in 0.in 0.5in 0.in,clip]{./figs/SSBM_experiments.pdf}
%         \caption{Scores on SSBM graphs}
%     \end{subfigure} \hfill
%     \begin{subfigure}[t]{0.47 \textwidth}
%         \centering
%         \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
%         \caption{Scores on \emph{CREMI-gridGraph} perturbed with noise}
%     \end{subfigure}

%     % \begin{subfigure}[t]{0.32 \textwidth}
%     %     \centering
%     %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
%     % \end{subfigure}\hfill
%     % \begin{subfigure}[t]{0.32 \textwidth}
%     %     \centering
%     %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
%     % \end{subfigure}
%     %     \begin{subfigure}[t]{0.49 \textwidth}
%     %     \centering
%     %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
%     %     \caption{No long-range predictions: \\$p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
%     % \end{subfigure} \hfill
%     % \begin{subfigure}[t]{0.49 \textwidth}
%     %     \centering
%     %     \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
%     %     \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
%     % \end{subfigure}
% \caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions. Solid lines represent median values over 30 experiments. Values between the 25th and the 75th percentile are shown in shaded areas. The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph. Experiments are performed on a crop of CREMI training sample B.
% \algname{} performances compared to spectral methods on synthetic graphs. The spectral methods were given the true number of clusters as input, in contrast to \algname{}. \TODO{Define paramters SSB; explain percentile stuff (for both noise experiments), user ARAND-error}
% }\label{fig:noise_plots}
% \end{figure}

### 2021-03-01 chapters/5_experiments_intro.tex
Small changes

\textbf{Grid-graphs from CNN predictions} -- We also evaluate the clustering methods on the task of neuron segmentation in EM image volumes using training data from the CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge}.
We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}\footnote{See Appendix \ref{sec:cremi_details} for all details about training and data augmentation.}. The predicted affinities $a_e\in[0,1]$, which represent how likely it is for a pair of pixels to belong to the same neuron segment, are then mapped to signed edge weights $w_e=a_e-0.5$, resulting in a 3D grid-graph having a node for each pixel/voxel of the  image\footnote{To map affinities to signed weights, we also tested the \emph{logarithmic mapping} proposed in \cite{finkel2008enforcing,andres2012globally}, but it performed worse in our experiments.}. We divided the three training samples of the CREMI challenge, which consists of approximately 196 million voxels each, into five sub-blocks for a total of 15 graph clustering problems (named \emph{CREMI-gridGraph} in Table~\ref{tab:datasets_and_energies}). 
% \TODO{long-range probs}

@@

        \begin{tabular}{l  c  r  c  c  c r r r r r r}
        \toprule
        Clustering problem & \makecell{Graph Type} & $\#I$ & $|V|$ & $|E|$ & GT & GAEC \cite{keuper2015efficient} & HCC-Sum & MWS \cite{wolf2018mutex} & HC-Avg & HCC-Avg \\ \midrule
        \emph{Modularity Clustering} \cite{brandes2007modularity} & \emph{complete} & 6& 34-115 & 561-6555 & \HollowBox & -0.457 & -0.453 & -0.073 & \textbf{-0.467} & \textbf{-0.467} \\ 
        \emph{Image Segmentation} \cite{andres2011probabilistic} & \emph{rag} & 100 & 156-3764 &  439-10970  & \HollowBox & \textbf{-2,955} & -2,953 & -2,901 & -2,903 & -2,896\\
        \emph{Knott-3D (150-300-450)} \cite{andres2012globally} & \emph{3D-rag} & 24 & 572-17k & 3381-107k & \HollowBox & \textbf{-36,667} & -36,652 & -35,200 & -35,957 & -35,631\\
        % \emph{Knott-3D-300} & \emph{3D-rag} & 8& & & \HollowBox\\
        % \emph{Knott-3D-450}& \emph{3D-rag} & 8 & & & \HollowBox\\  
        \emph{CREMI-3D-rag (OurCNN)}  & \emph{3D-rag} & 3& 134k-157k & 928k-1065k & \CrossedBox & \textbf{-1,112,287} & -1,112,286& -1,109,731 & -1,112,177 & -1,112,100\\ 
        \emph{Fruit-Fly Level 1-4} \cite{pape2017solving} & \emph{3D-rag} & 4& 5m-11m & 28m-72m & \HollowBox & \textbf{-151,022} & -151,017 & -150,879 & -150,909 & -150,876\\
        \emph{CREMI-gridGraph (OurCNN)} & \emph{gridGraph} & 15& 39m & 140m & \CrossedBox & -73,317,601 & -73,328,867 & -73,330,568 & \textbf{-73,502,947} & -73,474,856\\
        \emph{Fruit-Fly Level Global} \cite{pape2017solving} & \emph{3D-rag} & 1& 90m & 650m & \HollowBox & \textbf{-151,688} & -151,596 & -146,315 & -150,466 & -150,171 \\
        % \emph{(CREMI-pixGrid-LSIMasksUNet)} & \emph{gridGraph} & 1 & & 4 & \CrossedBox\\
        % \emph{(CityScapesValidation-pixGrid)} & \emph{gridGraph} &  &  & & \CrossedBox\\
        % \emph{CREMI-test....}\\\midrule
        % \emph{Stochastic Block Model (synthetic)} & \emph{non-planar} &-&- & - & \CrossedBox \\
        % \emph{(epinions and slashdot?)} & \emph{dense?} &  & & & \HollowBox\\

@@

    \caption{List of compared signed graph clustering problems: for each, we specify the number of instances $\# I$, nodes $|V|$, edges $|E|$, and whether a ground truth clustering is available. We compare algorithms in the \algname{} framework by evaluating which of the obtained clusterings is associated to the lowest value of the multicut objective defined in Eq.~\ref{eq:MC_objective} (\textbf{lower is better}).} 

@@

          & \makecell{ARAND\\Score} & \makecell{VOI\\split} & \makecell{VOI\\merge}&  \makecell{Runtime\\(s)} \\ \midrule 

@@

          & \makecell{CREMI\\Score} & \makecell{ARAND\\Score} & \makecell{VOI\\split} & \makecell{VOI\\merge}    \\ \midrule 

@@

    \caption{... We evaluate the algorithms by computing the Adapted Rand-Score (ARAND) and the Variation of Information Score (VI) \cite{arganda2015crowdsourcing}. And runtimes (\textbf{lower is better})}

@@

\caption{Dendograms built by GAEC, MWS, and HC-Avg on a small SSBM (two ground truth communities represented by colors). The dendrograms are truncated at the level of the clustering $\Pi^*$ returned by the algorithms.   \label{fig:dendrograms}}

@@

\textbf{Scores on CREMI instance-segmentation} -- 
SSBM graphs are \emph{non-planar} graphs, where every edge has the same probability to be present in the graph. On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: weather a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance). 
Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show that average linkage methods (HC-Avg, HCC-Avg) strongly outperforms other methods on \emph{CREMI-gridGraph} instances and also achieves the best scores on \emph{CREMI-3D-rag} graphs. Sum-based linkage methods (GAEC, HCC-Sum) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}). This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods does not work well on grid-graphs, because of the sparse local edge connections with strongly spatially-correlated noise (given that edge weights are predicted by a CNN)\footnote{This effect is not as strong on \emph{3D-rag} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}. 
The plot in Fig.~\ref{fig:noise_plots} confirms that HC-Avg and HCC-Avg perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (MWS). It is not a surprise that the AbsMax linkage used by MWS is not robust to this type of structured noise. However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} proves how MWS can achieve competitive performances with considerably lower runtimes.

\textbf{Results on CREMI challenge} -- 
Table~\ref{tab:cremi_leaderboard} shows how the \emph{HCC-Avg} and \emph{HC-Avg} clustering algorithms included in the proposed \algname{} framework achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
Most of other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs. As we also showed in Table ~\ref{tab:scores_3drag}, this approach considerably reduces the size of the clustering problem and, consequently, the post-processing time. 
On the other hand, our method achieves better performances by operating directly on pixels and removing in this way the parameter tuning necessary to obtain good super-pixels, which are usually highly dataset dependent.

% Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
% However: handcrafted and dataset dependent, performs better, no

@@

Specify that we divided samples into four blocks and then run the agglomeration again (moreover, run seeded WS to get rid of small segments).
Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights. 
Long-range connections are more noisy. 10\% represents a good compromise.
% then \algname{} with cannot-link constraints shows a clear tendency to over-cluster. \\

>>>>

\textbf{Grid-graphs from CNN predictions} -- We also evaluate the clustering methods on the task of neuron segmentation in EM image volumes using training data from the CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge}.
We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}\footnote{See Appendix \ref{sec:cremi_details} for all details about training and data augmentation.}. The predicted affinities $a_e\in[0,1]$, which represent how likely it is for a pair of pixels to belong to the same neuron segment, are then mapped to signed edge weights $w_e=a_e-0.5$, resulting in a 3D grid-graph having a node for each pixel/voxel of the  image\footnote{To map affinities to signed weights, we also tested the \emph{logarithmic mapping} proposed in \cite{finkel2008enforcing,andres2012globally}, but it performed worse in our experiments.}. 
\TODO{long-range 10\%} 
% Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights. Long-range connections are more noisy. 10\% represents a good compromise.
We divided the three training samples of the CREMI challenge, which consists of approximately 196 million voxels each, into five sub-blocks for a total of 15 graph clustering problems (named \emph{CREMI-gridGraph} in Table~\ref{tab:datasets_and_energies}).

@@

        \begin{tabular}{l  c  r  c  c  | r r r r r r}
        % \toprule
        &&&&\multicolumn{1}{c}{}&\multicolumn{5}{c}{Multicut objective values associated to final clusterings:} \\
        Clustering problem & \makecell{Graph Type} & $\#I$ & $|V|$ & $|E|$  & \multicolumn{1}{r}{GAEC \cite{keuper2015efficient}} & HCC-Sum & MWS \cite{wolf2018mutex} & HC-Avg & HCC-Avg \\ \midrule
        \emph{Modularity Clustering} \cite{brandes2007modularity} & \emph{complete} & 6& 34-115 & 561-6555 & % \HollowBox & 
        -0.457 & -0.453 & -0.073 & \textbf{-0.467} & \textbf{-0.467} \\ 
        \emph{Image Segmentation} \cite{andres2011probabilistic} & \emph{rag} & 100 & 156-3764 &  439-10970  & % \HollowBox 
        \textbf{-2,955} & -2,953 & -2,901 & -2,903 & -2,896\\
        \emph{Knott-3D (150-300-450)} \cite{andres2012globally} & \emph{3D-rag} & 24 & 572-17k & 3381-107k & % \HollowBox & 
        \textbf{-36,667} & -36,652 & -35,200 & -35,957 & -35,631\\
        % \emph{Knott-3D-300} & \emph{3D-rag} & 8& & & \HollowBox\\
        % \emph{Knott-3D-450}& \emph{3D-rag} & 8 & & & \HollowBox\\  
        \emph{CREMI-3D-rag (OurCNN)}  & \emph{3D-rag} & 3& 134k-157k & 928k-1065k % & \CrossedBox 
        & \textbf{-1,112,287} & -1,112,286& -1,109,731 & -1,112,177 & -1,112,100\\ 
        \emph{Fruit-Fly Level 1-4} \cite{pape2017solving} & \emph{3D-rag} & 4& 5m-11m & 28m-72m %& \HollowBox 
        & \textbf{-151,022} & -151,017 & -150,879 & -150,909 & -150,876\\
        \emph{CREMI-gridGraph (OurCNN)} & \emph{gridGraph} & 15& 39m & 140m %& \CrossedBox 
        & -73,317,601 & -73,328,867 & -73,330,568 & \textbf{-73,502,947} & -73,474,856\\
        \emph{Fruit-Fly Level Global} \cite{pape2017solving} & \emph{3D-rag} & 1& 90m & 650m % & \HollowBox 
        & \textbf{-151,688} & -151,596 & -146,315 & -150,466 & -150,171 \\
        % \emph{(CREMI-pixGrid-LSIMasksUNet)} & \emph{gridGraph} & 1 & & 4 & \CrossedBox\\
        % \emph{(CityScapesValidation-pixGrid)} & \emph{gridGraph} &  &  & & \CrossedBox\\
        % \emph{CREMI-test....}\\\midrule
        % \emph{Stochastic Block Model (synthetic)} & \emph{non-planar} &-&- & - & \CrossedBox \\
        % \emph{(epinions and slashdot?)} & \emph{dense?} &  & & & \HollowBox\\

@@

    \caption{List of compared signed graph clustering problems: for each, we specify the number of instances $\# I$, number of nodes $|V|$, and number of edges $|E|$. We compare algorithms in the \algname{} framework by evaluating which of the obtained clusterings is associated to the lowest value of the multicut objective defined in Eq.~\ref{eq:MC_objective} (\textbf{lower is better}).} 

@@

          & \makecell{ARAND\\error} & \makecell{VOI\\split} & \makecell{VOI\\merge}&  \makecell{Runtime\\(s)} \\ \midrule 

@@

          & \makecell{CREMI\\Score} & \makecell{ARAND\\error} & \makecell{VOI\\split} & \makecell{VOI\\merge}    \\ \midrule 

@@

    \caption{\textbf{(a-b)} Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-rag} clustering problems: average linkage methods performed best. Measures shown are Adapted-Rand error (ARAND, lower is better), Variation of Information \cite{arganda2015crowdsourcing} (VOI-merge for under-clustering error, VOI-split for over-clustering error, lower is better). \textbf{(c)} Current leading entries in the CREMI challenge leaderboard (March 2021). CREMI-score is given by geometric mean of (VOI-split + VOI-merge)  and adapted RAND error (lower is better).}

@@

\caption{Dendograms built by GAEC, MWS, and HC-Avg on a small SSBM (two ground truth communities represented by colors). The dendrograms are truncated at the level of the clustering $\Pi^*$ returned by the algorithms. \TODO{Update}  \label{fig:dendrograms}}

@@

\textbf{Scores on CREMI instance-segmentation} -- 
SSBM graphs are \emph{non-planar} graphs, where every edge has the same probability to be present in the graph. On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: weather a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance). 
Tables~\ref{tab:scores_3drag}-\ref{tab:scores_gridGraph} show that average linkage methods (\emph{HC-Avg}, \emph{HCC-Avg}) strongly outperforms other methods on \emph{CREMI-gridGraph} instances and also achieves the best scores on \emph{CREMI-3D-rag} graphs. Sum-based linkage methods (\emph{GAEC}, \emph{HCC-Sum}) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}). This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods does not work well on grid-graphs, because of the sparse local edge connections with strongly spatially-correlated noise (given that edge weights are predicted by a CNN)\footnote{This effect is not as strong on \emph{3D-rag} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}. 
The plot in Fig.~\ref{fig:noise_plots} confirms that \emph{HC-Avg} and \emph{HCC-Avg} perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (\emph{MWS}). It is not a surprise that the AbsMax linkage used by \emph{MWS} is not robust to this type of structured noise. However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} proves how \emph{MWS} can achieve competitive performances with considerably lower runtimes.

\textbf{Results on CREMI challenge} -- 
Table~\ref{tab:cremi_leaderboard} shows how the \emph{HCC-Avg} and \emph{HC-Avg} clustering algorithms included in the proposed \algname{} framework achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
Most of other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs. As we also showed in Table ~\ref{tab:scores_3drag}, this approach considerably reduces the size of the clustering problem and, consequently, the post-processing time. 
On the other hand, our method achieves better performances by operating directly on pixels (\emph{gridGraph+HCC-Avg}) and removes in this way the parameter tuning necessary to obtain good super-pixels, which are usually highly dataset dependent.
To scale up the clustering algorithms to the pixel-based problem given by the full test-volumes, we divided each volume into four sub-blocks, and then combined the resulting clusterings by running the clustering algorithms again on the combined graph.
% Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
% However: handcrafted and dataset dependent, performs better, no

@@

% To scale up the pixel-based aggSpecify that we divided samples into four blocks and then run the agglomeration again (moreover, run seeded WS to get rid of small segments).

% then \algname{} with cannot-link constraints shows a clear tendency to over-cluster. \\
